Stable quantum memories with limited measurement

### 2017-06-06 IsingECC/manuscript_ising_ecc_final.tex
Latest draft
Latest draft tex file with aforementioned changes

@@

@@

\title{Stable quantum memories with few measurements}
%\title{Finite temperature thresholds for stabilizer codes with few measurements}

@@

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:Intro}
%%%%%%%%%%%%%%%%%%%%%%

Quantum memories are an essential component for many quantum technologies, including quantum computing and quantum repeaters. In analogy to modern classical memories, one ideally wants a stable quantum memory that requires little or no active intervention and error correction. Unfortunately, no physical system that passively preserves quantum information indefinitely at finite temperatures and in an experimentally accessible number of dimensions is known \cite{Terhal:2015ks}. Instead, the operation of all known practical quantum memories require a combination of passive elements (i.e. dissipative cooling) and active measurement and correction cycles to keep quantum information protected.  In this work, we study the degree to which the amount of active measurement and correction can be reduced while maintaining quantum memory stability (our notion of stability, to be quantified later, corresponds to exponentially long lifetime for encoded states at some finite threshold temperature). We develop a new decoding and correction protocol that enables one to trim the number of measurements to a fraction of the complete set of measurements normally considered, and still maintain quantum memory stability.

We restrict our attention to quantum memories defined through stabilizer codes. For near term architectures, stabilizer codes\cite{Gottesman98} have emerged as the leading candidate for encoding quantum information and subsequent active error correction in quantum hardware, with small scale architectures actively being developed and deployed\cite{all the stabilizers}. \red{A tremendous amount of effort has gone into developing novel decoding schemes for stabilizer codes.  Cite Adrian Hutter, Harrington, Others.  More Background.}

 In previous work \cite{Freeman2014}, we analyzed the finite temperature dynamics of the toric code, verifying the well-known no-go theorems for the upper bound to the lifetime of the toric code at finite temperature \needcite.  Using this analysis, we were able to construct a measurement-free protocol for protecting the encoded qubits of the toric code \cite{Freeman2016}, but these protocols again were limited by the no-go theorems, and only provided a multiplicative constant increase to the lifetime.

Building off this previous work, here we examine the extent to which a limited amount of measurement can increase the lifetime of stabilizer codes with string-like excitations.  In sum, we demonstrate an algorithm that, for any constant density of measurements for a stabilizer code with stringlike excitations undergoing dissipation at a fixed temperature, a threshold can be achieved.  The threshold temperature scales with the amount of measurement used---fewer measurements result in a smaller threshold temperature, whereas more complete measurement raises the threshold temperature.  This tradeoff is commensurate with and complements what is known about decoding the stabilizer codes in the presence of \emph{noisy}, but complete measurements.

@@

where, for the remainder of the manuscript, unless explicitly stated otherwise, we assume $\Delta=1$.  This also fixes our units for temperature.  This is exactly the Hamiltonian version of the repetition stabilizer \emph{code}\cite{Freeman2016}.  Note that the terms $\sigma^i_z \sigma^{i+1}_z$ exactly correspond to the parity check stabilizer operators of the repetition code.  Confer with Table \ref{tab:code_vs_hamiltonian} for the correspondences between the stabilizer Hamiltonian and stabilizer code versions of the 1d Ising model.

@@

In the parlance of the 1D Ising model, bit flip errors are often also classified via the dual variables called \emph{domain walls}.  Domain walls are simply locations on the 1D Ising chain where a stabilizer operator yields a measurement of $-1$---i.e., locations where neighboring spins point in different directions.  With periodic boundary, the number of these locations is always a multiple of two, and a single bit flip event either creates a pair of such domain walls, deletes a pair of domain walls, or causes a domain wall to translate by one unit.

Whether considered as a code or as a Hamiltonian, the condition for whether a state of the system with errors present can be reliably returned to an encoded state is the same: so long as less than half the system has had errors, a majority rule decoder that has access to measurements of the full set of stabilizers ${\sigma^i_z \sigma^{i+1}_z}$ will reliably be able to correctly remove errors.  When errors are completely independent (i.e., at very high temperature), we can define random variables $x_i=1$ when an error occurs on site $i$, and $0$ otherwise.  If these errors occur with probability $p$ on each spin, independently at random every error detection cycle, then Chernoff's bound gives an upper bound to the probability of an error in the encoded space, $P(\Sigma_i x_i \geq L/2) \leq \rm{exp}[-Lp\frac{\delta^2}{2+\delta}]$ for $\delta=1/2p-1$.  Thus, for complete measurement, errors in the encoded subspace are exponentially suppressed in system size, so long as the error rate is sufficiently small.

@@

\begin{equation}
\left \{ c_\omega \right \} = \left \{ \sqrt{\gamma(0)} T_{b}, \sqrt{\gamma(1)} D^\dagger_{b}, \sqrt{\gamma(-1)} D_{b} \right\} 
\end{equation}
where $D_{b}$ dissipates a pair of domain walls,  $D^\dagger_{b}$ creates a pair of domain walls, $T_{b}$ translates a domain wall by one unit, and $\gamma(\cdot)$ is a rate function dependent on the details of the bath.  This bath is chosen to model the dynamics of local, single bit-flip errors.  In the Pauli basis, these operators take the following form.

@@

 Contrariwise, thresholds at finite temperature are usually quoted in terms of a critical \emph{temperature}.  That is, there must exist some critical temperature $T_c$ below which codes can be reliably corrected.  Unfortunately, this definition obscures a great deal of physics---different choices of bath model can greatly affect the dynamics of the error processes, to the extent that a quoted ``critical temperature'' often implicitly specifies a choice of bath model.  Because different bath interactions can give rise to different system dynamics, the choice of bath also directly affects the strategy used for error correction.  For example, it is known that the toric code's threshold temperature is altered by considering a correlated bath \red{time or space correlated?} rather than an uncorrelated one \cite{Novais13}.

 The main consequence of choosing an Ohmic bath is that it sets the amplitude of the excitation hopping process.  That is, $\gamma(0)$ is determined by the $\omega \rightarrow 0$ limit of the spectral density of the bath, and for the Ohmic bath taking the $\omega\rightarrow0$ limit of  Eq. \ref{eq:gammadef} yields $\gamma(0) \sim T$. 
Ultimately, this means that the hopping rate of domains walls is controlled by this choice of bath model. At finite temperatures, this introduces correlations into the patterns of errors that effect the system, and so it is no longer possible to talk about an ``independent error probability per site''. 
In contrast to the behavior of $\gamma(0)$, 
the other operationally important feature of the bath, the ratio of domain wall creation and annihilation rates, is set by detailed balance to Boltzmann-like scaling (i.e., $\gamma(1)/\gamma(-1) = \exp(-1/T)$), and is independent of the choice of bath spectrum.

 In the most extreme case, at sufficiently low temperature, errors are most often immediately dissipated by the bath upon creation.  However, because domain walls that are not immediately adjacent cannot be dissipated by the bath, the system occasionally becomes ``trapped'' in the first excited state by a rare pair creation followed by pair hopping event -- i.e., a $D^\dagger_{b}$ followed by a $T_{b}$ -- before the bath can dissipate the excitation.  Then any subsequent errors are overwhelmingly more likely to act on existing pair of domain walls, translating them around in a one-dimensional random walk.

 Thus, error correction for the 1D Ising model at low temperature with this sort of bath dynamics is equivalent to attempting to identify these randomly-migrating rare pairs of domain walls.  While a majority-rule decoding scheme works in both low and high temperature limits for the Ising model, if the number of measurement resources is restricted, the standard majority rule scheme breaks down.

@@

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{detect_swap.pdf}}
\end{center}
\caption{This cartoon illustrates the ``centering'' procedure for detected defects.  Spin variables are in gray, and domain wall variables are in blue (no defect present) and red (defect present).  When a defect is detected on a measurement patch (blue box), it is swapped to the center of the measurement patch via the $\rm{DSWAP}$ operator (black arrows).  The defect immediately adjacent to it is also swapped onto the measurement patch so as not to pull apart defect pairs that would have otherwise dissipated.}
\label{fig:detect_swap}
\end{figure}

@@

The centering process aids the probability of fusion calculation by ensuring that the coordinates and measurement times are representative of when and where defects are actually created.  If defects escape from measurement patches, then upon being measured again, the time recorded by the measurement patch now underestimates how old the defect actually is, biasing the probability estimate.  This centering operation greatly reduces the probability of defect escape.

 Note that the pattern of $\rm{DSWAP}s$ used in \figref{fig:detect_swap} also swaps the neighboring, \emph{unmeasured} defect onto the measurement patch.  This is to ensure that the protocol does not inadvertently create a new separated pair of domain walls in the system by shifting only one domain wall in a potentially adjacent pair.

@@

To calculate this probability, we proceed via Bayes rule: 
\begin{align}
\label{eq:bayes}
&P(d_1:d_2 | d_1^{x_1,t_1} \wedge d_2^{x_2,t_2}) = \\ \notag
&\frac{P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) P(d_1 : d_2)}{P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})}
\end{align}
The individual terms on the right hand side of equation \ref{eq:bayes} are straightforward to interpret.  $P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2)$ represents the probability that two measured defects would be at $(x_1,t_1)$ and $(x_2,t_2)$ given that they are indeed a pair.  This can be related to the probability that a one dimensional diffusion process with diffusion constant $D$ will perform an excursion of distance $|x_2-x_1|$ or greater in a time $t_2 - t_1$; \textit{i.e.,} will perform an excursion that can measurement patches at $x_1$ and $x_2$. Explicitly,
\begin{align}
\label{eq:bayesformula}
&P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) \\ \notag
&= 1-2\int_{0}^{|x_2-x_1|} dx \frac{1}{2\pi D |t_2-t_1|} \rm{exp}\bigg(-\frac{|x_2-x_1|^2}{2 D |t_2-t_1|}\bigg) \\ \notag 
&= 1 - {\rm erf}\bigg(\frac{|x_2-x_1|}{2\sqrt{D |t_2 - t_1|}}\bigg) 
\end{align}
For our analysis, we will choose $D\propto \gamma_0$.  The exact correspondence between $D$ and $\gamma_0$ depends on the details of the error correction algorithm itself, so, in practice, we treat the constant of proportionality as an empirically tuned parameter.  Furthermore, we approximate any detected defects as arising from a pair that was created an equal distance between the measurement patches at locations $x_1$ and $x_2$ for the purposes of calculating the probability in Eq. \ref{eq:bayesformula}.

@@

 \subsection{Common error modes and analysis}
 \label{sec:threshold}

 The two primary failure modes of the error correction procedure are (1) defects escaping measurement patches, and (2) defects being paired incorrectly. These failure modes become more harmful as temperature increases.  Failure mode 1 can be suppressed by working with large measurement patches, as the escape timescale is exponential in the number of sites within the measurement patch---i.e., it scales like $(1/\gamma_0)^{\rm{\#\ of\ sites\ on\ patch}}$.  Failure mode 2 can be suppressed to a degree, but at high enough temperature, will eventually happen with high probability, as is the case in the full-measurement version of the protocol.  If too many errors are introduced between measurement cycles, it becomes impossible to correct the system even in principle because the syndrome measurements can no longer be unambiguously decoded.  At sufficiently low temperature, however, with some assumptions, our algorithm can extend the lifetime of the system exponentially in system size.

 Suppose that (a) defects are efficiently trapped by the measurement patches, and (b) temperature is low so that there is $\rho \ll 1$ defect pair per measurement patch.  In this regime, condition (a) guarantees that defects do not escape measurement patches.  Then, the only error pathway is a sequence of incorrect, but nonetheless ``plausible'' error correction operations, whereby some sdefects are paired with defects that are not their own pair.  
%************************Make explicit here that it's a heuristic argument.  Because the error processes in our model are difficult to etc. etc. etc.
 To upper bound this error rate, note that such erroneous pairing occurs because one member of a paired defect has not yet been measured.  In other words, one defect of a pair is measured, and the other defect spends ``too long'' migrating around in the unmeasured bulk region.  Suppose that the average amount of time a defect spends sitting on a measurement patch is $\tau_s$, and the average time it takes a defect to be detected on a measurement patch, after creation, is $\tau_d$.  Further suppose $\tau_s/\tau_d = \delta \ll 1$---that is, on average, defects are unlikely to escape from a measurement patch over the timescale it takes a defect to migrate within the bulk region to a measurement patch.

 Treating the full dynamics of errors is difficult, so we first consider a different, simpler error dynamics.  First, we argue how, in the presence of this simpler error model, our algorithm provides an exponentially long lifetime in system size.  Then, we argue how this simpler error model is actually more pessimistic with respect to possible error processes than the true error dynamics---that is, we expect the real model to have a \emph{better} lifetime scaling than would be expected from the simple error model.

 The simple error model is defined as follows:  suppose that a single pair of defects is in a system, and that no new pairs will be introduced.  One of the pair is fixed on a measurement rail, and the other is, at time 0, undetected.  Further, suppose that there is an error process that occasionally translates the unmeasured defect by an amount $2\sqrt{\gamma_0 \delta t}$, for hopping rate $\gamma_0$ and for system time $\delta t$.  Note that this means the error process acts on longer distance scales as system time increases.  The particular form of this error process is chosen to mimic a spurious error correction event, where a pair of defects is ``corrected'', but this pair of defects was not a real pair, leaving another unmeasured defect even further away.  As time increases, the characteristic distance over which this error process could occur also increases, in accordance with the typical pair-wise separation between two defects performing a random walk.  This typical distance is exactly the factor used by the error correction algorithm to determine if a pair of defects should be corrected or not.  Thus, the error process is representative of a worst case error correction event that not only pairs the wrong two defects, but leaves the system in a configuration with an unmeasured defect as far separated from the measured defect as possible.

 If this error process happens every $\tau_{\epsilon}$, then an uncorrectable error will occur if the bulk defect remains undetected up until it crosses half the system.  For patches of size $\lambda$, the probability that this occurs is roughly $(\tau_{\epsilon} / \tau_d)^{k}$, where $k$ is the number of times the error process must occur for the error process to have separated the defects a distance $(L/2\lambda)$ and $\tau_d$ is the timescale associated with a non-erroneous error correction operation.  Because this error process happens approximately every $\tau_{\epsilon}$, after a timescale $q*\tau_{\epsilon}$, the defect pairs will have been separated a distance $\Sigma^q_{i=1} \sqrt{i * \gamma_0 \tau_{\epsilon}}$, assuming that they are never correctly paired.  This sum $\Sigma^q_{i=1} \sqrt{i}$ grows asymptotically like $q^{3/2}$.  Thus, $k$ then scales approximately like $(L/\lambda)^{2/3}$.

 Finally, if we have $L/\lambda$ such simultaneous error processes independently in the system---one for each measurement patch---then the total error probability scales like
\begin{align}
\label{eq:err_scaling}
 P(\rm{uncorrectable\ error}) \leq (L/\lambda) (\tau_{\epsilon} / \tau_d)^{(L/\lambda)^{2/3}}.
\end{align}

For this system, $\tau_{\epsilon}$ is much smaller than $\tau_d$, thus the full probability of erroneous corrective operations is exponentially small in system size.

 This probability serves as an upper bound because it is extremely pessimistic about the sorts of error processes occurring.  Note that in the real system, a spurious error correction process that effectively increases the distance between a pair of defects also reduces the total number of defects by two.  Thus, while our toy error model is ``non-interacting''---that is, it assumes $L/\lambda$ independent error processes which, in sum, take the form described in Eq. \ref{eq:err_scaling}---a more careful treatment of the error process, including interactions between defects, as in the real model, would result in an error probability \emph{smaller} than the one calculated here.

 In the following section, we provide numerical evidence that the lifetime of the Ising model in the presence of the protocol scales quasi-exponentially with the number of measurement patches, as anticipated by the upper bound in Eq.\ref{eq:err_scaling}.

@@

>>>>

\newcommand{\te}{\tau_{\rm{esc}}}
\newcommand{\Tau}{\mathrm{T}}

@@

\newcommand{\CMH}[1]{{\color{green} { #1}}}
\newcommand{\CDF}[1]{{\color{red} {( #1)}}}

@@

\title{Stable quantum memories with limited measurement}
%\title{Finite temperature thresholds for stabilizer codes with few measurements}

@@

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:Intro}
%%%%%%%%%%%%%%%%%%%%%%
 Quantum memories are an essential component for many quantum technologies, including quantum computing and quantum repeaters. In analogy to modern classical memories, one ideally wants a stable quantum memory that requires little or no active intervention and error correction. Unfortunately, no physical system that passively preserves quantum information indefinitely at finite temperatures and in an experimentally accessible number of dimensions is known \cite{Terhal:2015ks}. Instead, the operation of all known practical quantum memories require a combination of passive elements (i.e. dissipative cooling) and active measurement and correction cycles to keep quantum information protected.  In this work, we study the degree to which the amount of active measurement and correction can be reduced while maintaining quantum memory stability (our notion of stability, to be quantified later, corresponds to exponentially long lifetime for encoded states at some finite threshold temperature). We develop a new decoding and correction protocol that enables one to trim the number of measurements to a fraction of the complete set of measurements normally considered, and still maintain quantum memory stability.

 We restrict our attention to quantum memories defined through stabilizer codes. For near term architectures, stabilizer codes\cite{Gottesman98} have emerged as the leading candidate for encoding quantum information and subsequent active error correction in quantum hardware, with small scale architectures actively being developed and deployed\cite{all the stabilizers}.  A tremendous amount of effort has gone into developing novel decoding schemes for stabilizer codes, particularly the toric code.  Different schemes often emphasize different decoding features, like efficient decoding\cite{Kovalev2013,Wang2009,Duclos-Cianci2010}, locality\cite{Breuckmann2016,Torlai2016,Harrington2004,Herold2014}, robustness to particular sorts of noise\cite{Novais2013,Bombin2012,Wootton2015}, or use of dissipation\cite{Freeman2016,Hutter2012a,Hutter2014,Fujii2014,Pedrocchi2013,Pedrocchi2011,Chesi2010a,Chesi2010b,Hamma2009,Herdman2010, Weimer2010, Dengis2014, Kapit2015, Bardyn2015}.

 In previous work \cite{Freeman2014}, we analyzed the finite temperature dynamics of the toric code, verifying the well-known no-go theorems for the upper bound to the lifetime of the toric code at finite temperature\cite{Bravyi2009, Alicki2009a, Chesi2010b, Yoshida2011b, Hastings2011a, Landon-Cardinal2013, Temme2014, temme2015fast}.  Using this analysis, we were able to construct a measurement-free protocol for protecting the encoded qubits of the toric code \cite{Freeman2016}, but these protocols again were limited by the no-go theorems, and only provided a multiplicative constant increase to the lifetime.

 Building off this previous work, here we examine the extent to which a limited amount of measurement can increase the lifetime of stabilizer codes with string-like excitations.  In sum, we demonstrate an algorithm that, for any constant density of measurements for a stabilizer code with stringlike excitations undergoing dissipation at a fixed temperature, a threshold can be achieved.  The threshold temperature scales with the amount of measurement used---fewer measurements result in a smaller threshold temperature, whereas more complete measurement raises the threshold temperature.  This tradeoff is commensurate with and complements what is known about decoding the stabilizer codes in the presence of \emph{noisy}, but complete measurements\cite{Nickerson2016}.

@@

where, for the remainder of the manuscript, unless explicitly stated otherwise, we assume $\Delta=1$.  This is exactly the Hamiltonian version of the repetition stabilizer \emph{code}\cite{Freeman2016}.  Note that the terms $\sigma^i_z \sigma^{i+1}_z$ exactly correspond to the parity check stabilizer operators of the repetition code (see Table \ref{tab:code_vs_hamiltonian}).

@@

In the parlance of the 1D Ising model, bit flip errors are often also classified via the dual variables called \emph{domain walls} or defects.  Defects are simply locations on the 1D Ising chain where a stabilizer operator yields a measurement of $-1$---i.e., locations where neighboring spins point in different directions.  With periodic boundary, the number of these locations is always even, and a single bit flip event either creates a pair of such defects, deletes a pair of defects, or causes a defect to translate by one unit.

So long as less than half the system has had errors, a majority rule decoder that has access to measurements of the full set of stabilizers ${\sigma^i_z \sigma^{i+1}_z}$ will reliably be able to correctly remove errors.  When errors are completely independent (i.e., at very high temperature), we can define random variables $x_i=1$ when an error occurs on site $i$, and $0$ otherwise.  If these errors occur with probability $p$ on each spin, independently at random every error detection cycle, then Chernoff's bound gives an upper bound to the probability of an error in the encoded space, $P(\Sigma_i x_i \geq L/2) \leq \rm{exp}[-Lp\frac{\delta^2}{2+\delta}]$ for $\delta=1/2p-1$.  Thus, for complete measurement, errors in the encoded subspace are exponentially suppressed in system size, so long as the error rate is sufficiently small.

@@

\begin{equation}
\left \{ c_\omega \right \} = \left \{ \sqrt{\gamma(0)} T_{b}, \sqrt{\gamma(1)} D^\dagger_{b}, \sqrt{\gamma(-1)} D_{b} \right\} 
\end{equation}
where $D_{b}$ dissipates a pair of defects,  $D^\dagger_{b}$ creates a pair of defects, $T_{b}$ translates a defect by one unit, and $\gamma(\cdot)$ is a rate function dependent on the details of the bath.  This bath is chosen to model the dynamics of local, single bit-flip errors.  In the Pauli basis, these operators take the following form.

@@

 Contrariwise, thresholds at finite temperature are usually quoted in terms of a critical \emph{temperature}.  That is, there must exist some critical temperature $T_c$ below which codes can be reliably corrected.  Unfortunately, this definition obscures a great deal of physics---different choices of bath model can greatly affect the dynamics of the error processes, to the extent that a quoted ``critical temperature'' often implicitly specifies a choice of bath model.  Because different bath interactions can give rise to different system dynamics, the choice of bath also directly affects the strategy used for error correction.  For example, it is known that the toric code's threshold temperature is altered by considering a space-correlated bath rather than an uncorrelated one \cite{Novais2013}.

 The main consequence of choosing an Ohmic bath is that it sets the amplitude of the excitation hopping process.  That is, $\gamma(0)$ is determined by the $\omega \rightarrow 0$ limit of the spectral density of the bath, and for the Ohmic bath taking the $\omega\rightarrow0$ limit of  Eq. \ref{eq:gammadef} yields $\gamma(0) \sim T$. 
Ultimately, this means that the hopping rate of domains walls is controlled by this choice of bath model. At finite temperatures, this introduces correlations into the patterns of errors that effect the system, and so it is no longer possible to talk about an ``independent error probability per site''. 
In contrast to the behavior of $\gamma(0)$, 
the other operationally important feature of the bath, the ratio of defect creation and annihilation rates, is set by detailed balance to Boltzmann-like scaling (i.e., $\gamma(1)/\gamma(-1) = \exp(-1/T)$), and is independent of the choice of bath spectrum.

 In the most extreme case, at sufficiently low temperature, pairs of neighboring defects are most often immediately dissipated by the bath upon creation.  However, if a pair creation is followed by pair hopping event -- i.e., a $D^\dagger_{b}$ followed by a $T_{b}$ -- the error can no longer be immediately dissipated by the local action of the bath.  Subsequently the defects will undergo a one-dimensional random walk, and topologically non-trivial random walks will cause uncorrectable logical errors.

 Thus, error correcting the 1D Ising model at low temperature with this sort of bath dynamics reduces to attempting to identify these randomly-migrating rare pairs of defects.  While a majority-rule decoding scheme works in both low and high temperature limits for the Ising model, if the number of measurement resources is restricted, the standard majority rule scheme breaks down because of the intrinsic uncertainty regarding unmeasured defects.

@@

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{detect_swap.pdf}}
\end{center}
\caption{This cartoon illustrates the ``centering'' procedure for detected defects on a unit cell.  Spin variables are in gray, and domain wall variables are in blue (no defect present) and red (defect present).  When a defect is detected on a measurement patch (blue box), it is swapped to the center of the measurement patch via the $\rm{DSWAP}$ operator (black arrows).  The defect immediately adjacent to it is also swapped onto the measurement patch so as not to pull apart defect pairs that would have otherwise dissipated.}
\label{fig:detect_swap}
\end{figure}

@@

The centering process aids the probability of fusion calculation by ensuring that the coordinates and measurement times are representative of when and where defects are actually created.  If defects escape from measurement patches, then upon being measured again, the time recorded by the measurement patch now underestimates how old the defect actually is, biasing the probability estimate.  This centering operation greatly reduces the probability of defect escape.  This systematic underestimate of defect lifetimes can be fixed by a more elaborate record keeping protocol (See Appendix \ref{sec:appendix_fix_long_errors}).

 Note that the pattern of $\rm{DSWAP}s$ used in \figref{fig:detect_swap} also swaps the neighboring, \emph{unmeasured} defect onto the measurement patch.  This is to ensure that the protocol does not inadvertently create a new separated pair of defects in the system by shifting only one defect in a potentially adjacent pair.

@@

To calculate this probability, we proceed via Bayes rule: 
\begin{align}
\label{eq:bayes}
&P(d_1:d_2 | d_1^{x_1,t_1} \wedge d_2^{x_2,t_2}) = \\ \notag
&\frac{P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) P(d_1 : d_2)}{P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})}
\end{align}
The individual terms on the right hand side of equation \ref{eq:bayes} are straightforward to interpret.  $d_i^{x_i,t_i}$ indicates a defect residing on measurement patch $i$ with spacetime coordinate $x_i,t_i$.  $P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2)$ represents the probability that two measured defects would be at $(x_1,t_1)$ and $(x_2,t_2)$ given that they are indeed a pair.  This can be related to the probability that a one dimensional diffusion process with diffusion constant $D$ will perform an excursion with a displacement $|x_2-x_1|$ or greater in a time $t_2 - t_1$; \textit{i.e.,} will perform an excursion that can reach measurement patches at $x_1$ and $x_2$. Explicitly,
\begin{align}
\label{eq:bayesformula}
&P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) \\ \notag
&= 1-2\int_{0}^{|x_2-x_1|} dx \frac{1}{2\pi D |t_2-t_1|} \rm{exp}\bigg(-\frac{|x_2-x_1|^2}{2 D |t_2-t_1|}\bigg) \\ \notag 
&= 1 - {\rm erf}\bigg(\frac{|x_2-x_1|}{2\sqrt{D |t_2 - t_1|}}\bigg) 
\end{align}
For our analysis, we will choose $D\propto \gamma_0$.  The exact correspondence between $D$ and $\gamma_0$ depends on the details of the error correction algorithm itself, so, in practice, we treat the constant of proportionality as an empirically tuned parameter.  Furthermore, we approximate any detected defects as arising from a pair that was created an equal distance between the measurement patches at locations $x_1$ and $x_2$ for the purposes of calculating the probability in Eq. \ref{eq:bayesformula}.

@@

 \subsection{Error dynamics}

  In this section, we derive the error rate for a simple error model.  While this error model does not account for the complete error dynamics of the full 1D Ising model in the presence of our protocol, we argue how it nonetheless serves as an upper bound to the true error dynamics.  Finally, we sketch how this protocol provides a threshold for any finite density of measurements.

 \subsubsection{A simple error model}
 \label{sec:threshold}

 The simplified error model is defined as follows:  suppose that a single pair of defects is in the system, and that no new pairs will be introduced.  One of the pair is fixed on a measurement patch, and the other is, at time 0, undetected and residing somewhere in the bulk between measurement patches.  We will model spurious error correction by an error process that translates the unmeasured defect by a distance $2\sqrt{\gamma_0 \delta t}$.  As time increases, the characteristic distance over which this error process can occur also increases, in accordance with the typical pair-wise separation between two defects performing a random walk.  This typical distance is exactly the factor used by the error correction algorithm to determine if a pair of defects should be corrected or not.  Thus, the error process is representative of a worst case error correction event that not only pairs the wrong two defects, but leaves the system in a configuration with an unmeasured defect as far separated from the measured defect as possible.

 An uncorrectable error will occur if the bulk defect remains undetected up until it crosses half the system.  For patches of size $\lambda$, the probability that this occurs is roughly $(\tau_{\epsilon}^{-1} / \tau_d^{-1})^{k}$, where $k$ is the number of times the error process must occur for the error process to have separated the defects a distance $(L/2\lambda)$, $\tau_{\epsilon}^{-1}$ is the rate of the error process and $\tau_d^{-1}$ is the rate of a non-erroneous error correction operation.  In the worst case, after a timescale $q\cdot\tau_{d}$, the defect pairs will have been separated a distance 
\begin{equation}  
\Sigma^q_{i=1} \sqrt{i \cdot \gamma_0 \tau_{d}}
\end{equation}
 assuming that they are never correctly paired.  This sum grows asymptotically like $q^{3/2}$, thus, $k$ scales approximately like $(L/\lambda)^{2/3}$.
Finally, assuming there are $L/\lambda$ such simultaneous independent error processes in the system---one for each measurement patch---then the total error probability scales like
\begin{align}
\label{eq:err_scaling}
 P(\rm{error})\leq (L/\lambda) (\tau_{\epsilon}^{-1} / \tau_d^{-1})^{(L/\lambda)^{2/3}}.
\end{align}
For sufficiently low temperatures (see Sec. \ref{sec:correspondence}), $\tau_{\epsilon}^{-1}$ is much smaller than $\tau_d^{-1}$, thus the full probability of erroneous corrective operations is exponentially small in system size.

 \subsubsection{Correspondence between model and full error dynamics}
 \label{sec:correspondence}

 In this section, we detail the approximations that are necessary to map the error dynamics of the simple model to the full error dynamics of the 1D Ising model in the presence of our protocol.  The primary approximations made are concerning \textbf{(1)} fast defect detection, \textbf{(2)} accurate pairing, \textbf{(3)} defects escaping measurement patches, and \textbf{(4)} defect interactions.

 \textbf{(1)}. If defects are produced in between measurement patches faster than they are detected, then this algorithm cannot in principle correct errors.  Thus, we require that the characteristic diffusion time for defects in the bulk to migrate to a measurement patch, $\gamma_0^{-1}(\lambda_b)^2$, to be much shorter than the characteristic timescale over which a pair of defects is created in the bulk, $\gamma_0^{-1} \exp{\Delta/T}$.  Thus, working at low temperature ensures this approximation.

 \textbf{(2)}. If defects are paired incorrectly more often than they are paired correctly, then the algorithm will fail.  To ensure that $(\tau_{\epsilon}^{-1} / \tau_d^{-1})\leq1$ (see Eq. \ref{eq:err_scaling}), we must work in the diffuse limit, where the average number of defects per unit cell is much less than $1$.  This is equivalent to $\lambda \gamma_+<<1$.  This ensures that, when defects are being processed by the algorithm, that more often than not, defects will be correctly paired simply because it's unlikely there are any other defects nearby.  Thus, assuming condition (1)---that defects are detected quickly---defect pairs satisfying Eq. \ref{eq:bayesformula} are more likely than not to be genuine pairs.

 \textbf{(3)}. While the simple model does not account for defects escaping measurement patches, this can occur in the real system when a series of translation events occurs between measurements.  For a measurement rate $\chi$, these processes are of $O(\gamma_+ (\gamma_0/\gamma_-) (\gamma_0/\chi)^{\lambda_m/2})$, for measurement patches of size $\lambda_m$, assuming $\chi > \gamma_0$.  Thus, this process can be suppressed by working with a larger sized measurement patch, or with a measurement rate suitably larger than the intrinsic translation rate of the system, $\gamma_0$.  At worst, the age of defects that escape measurement patches but that are subsequently recaptured may be underestimated by the algorithm, because the ``age'' of the defect would be erroneously reset to zero.  This would then erroneously underestimate the distance the algorithm would plausibly search for a pairing defect---i..e, the denominator of the error function in Eq. \ref{eq:bayesformula} could be artificially small because the ``real'' defect age is actually older.

 In principle, because defects have some constant rate of escape from measurement patches, this sets a maximum correctible distance for the algorithm.  If we denote the timescale over which these escapes occur on average as $\te$, then one of a defect in a pair that is separated by much more than $\sqrt{D \te}$ will be overwhelmingly likely to escape from its measurement patch before the denominator of \ref{eq:bayesformula} can grow large enough to match the defect to its pair---potentially spoiling the system size scaling of the algorithm.

 In practice, by occasionally scaling the size of the measurement patches, $\lambda_m$, keeping the ratio of measured sites to unmeasured sites fixed, this maximum distance can be tuned larger.  For our simulations, we did not need to perform this measurement patch scaling, because the rate of defect escape was so small, even for $\lambda_m=3$.  Care must be taken, however, because measurement patches cannot be made arbitrarily large without violating the condition mentioned in point \textbf{(2)}.  To properly account for these sorts of errors, a more involved algorithm must be used which more accurately estimates defect lifetimes.  We provide such a modified algorithm that corrects these rare long-distance errors without any additional measurement resources in Appendix \ref{sec:appendix_fix_long_errors}.  We emphasize, however, that the gains from using such an algorithm would only be apparent at length scales considerably larger than those studied in this manuscript.

 \textbf{(4)}. In reality, the defects can annihilate without the protocol intentionally pairing them.  To leading order, at low temperature, these processes are ``self-correcting''.  That is, a pair of neighboring defects enters the system, and then is subsequently annihilated.  In principle, it is possible for a sequence of $k$ free pairs of defects to appear in the bulk---one pair per unit cell---of which, $k-1$ are then subsequently erroneously ``corrected'', resulting in two defects separated by a distance $k \lambda$, but this process is exponentially slow in the average defect unit cell density, which we already choose to be small via condition \textbf{(2)}.  That is, the error rate due to the erroneous  separation of defects by a distance $\lambda k$ is $\propto(\lambda \gamma_+)^k$.

 Additionally, defect interactions actually \emph{decrease} the number of defects in the system.  Thus, while our toy error model is ``non-interacting''---that is, it assumes $L/\lambda$ independent error processes which, in sum, take the form described in Eq. \ref{eq:err_scaling}---a more careful treatment of the error process, including interactions between defects, as in the real model, would result in an error probability \emph{smaller} than the one calculated here.  In Sec. \ref{sec:experiments}, we provide numerical evidence that the lifetime of the Ising model in the presence of the protocol scales exponentially with the number of measurement patches, as anticipated by the upper bound in Eq.\ref{eq:err_scaling}.

 \subsubsection{Error correction at any measurement density}
 \label{sec:ecc_any_m}

 A key feature of the protocol is the ability to provide an error correcting threshold at any finite measurement density.  In particular, for a fixed measurement density $m$, and fixed measurement and bulk length scales $\lambda_m$ and $\lambda_b$, respectively, it is still possible to satsify the rate assumptions of Sec. \ref{sec:correspondence} by tuning temperature sufficiently low.  Each rate assumption does not explicitly depend on total system size $L$, only unit cell size $\lambda$.

 In practice, larger $\lambda_b$ (alternatively, smaller $m$) will result in lower threshold temperatures simply because the temperature must be lower to satisfy the rate assumptions of conditions \textbf{(1)} and \textbf{(2)}.  We provide explicit evidence of this scaling in Fig. \label{fig:CriticalTempVsMeasurementFraction}.

@@

\appendix
%%%%%%%%%%%%%%%%%%%%%%
\section{Alternative Algorithm for Estimating Defect Lifetimes}
\label{sec:appendix_fix_long_errors}
%%%%%%%%%%%%%%%%%%%%%%
